The title

### 2019-07-31 README.Rmd
added tibble of scan regions

```{r example}
#library(qtl2hotspots)
## basic example code
```

>>>>

```{r example}
map <- readRDS(here::here("analysis", "data", "derived_data", "map.rds"))
hot_chr <- c(2, 5, 7, 11, 13)
start_index <- c(3742, 3498, 927, 1868, 2814) # from s1 values in condor submit files
scan_length <- c(247, 269, 242, 217, 226) # in number of markers, from condor submit files
stop_index <- start_index + scan_length - 1 # index of the last marker in the interval
start_position <- c(map$`2`[start_index[1]], 
                    map$`5`[start_index[2]], 
                    map$`7`[start_index[3]],
                    map$`11`[start_index[4]],
                    map$`13`[start_index[5]]
)
stop_position <- c(map$`2`[stop_index[1]], 
                    map$`5`[stop_index[2]], 
                    map$`7`[stop_index[3]],
                    map$`11`[stop_index[4]],
                    map$`13`[stop_index[5]]
)
tibble::tibble(hot_chr, start_index, scan_length, stop_index, start_position, stop_position)
```
